|

### 2022-05-01 paper/paper.Rmd
Update paper.Rmd

>>>>

The following functions are implemented in the Mathematica package {\tt mmtour.wl}

\begin{itemize}

\item ProjectionPlot[data, projmat, xRange(=Automatic), yRange(=Automatic), 
colour(=Automatic)] with arguments

\begin{itemize}
\item data: A list of data matrices (they must all have the same dimensionality)
\item projmat: A projection matrix which describes the projection plane. This is the 
initial projection and does not neet by orthonormal.
\item xRange: A list which details the range of the horizontal axis.
\item yRange: A list which details the range of the vertical axis.
\item colour: A list of graphics directives to be applied to each data \
matrix.
\end{itemize}

There are problems with the default values for x and y ranges and colour. It would be 
better to fix the ranges and colour based on the data as well as the origin of axes 
and the size of the points.

The format for the printed projection matrix can be improved also. Maybe fix the 
number of digits and the position of the label.

\item SlicePlot[data, projmat, centrePoint, height, heightRange, 
ptSize1(=0.005), ptSize2(=0.004), minDist(=0)] with arguments (used to be called SliceDynamic in Alex's first version, the name SliceDynamic was taken by something else below)

\begin{itemize}
\item data: A data matrix
\item projmat: The inital projection matrix
\item centrepoint: The initial position of the slice
\item height: The initial height of the slice
\item heightRange: The range of heights
\item ptSize1: The size of the points that exist within the slice
\item ptSize2: The size of the points that exist outside of the slice
\end{itemize}

This function requires some auxiliary functions. It does not accept more than one data set.

\end{itemize}
